The pragmatics of perspective-taking

### 2018-05-14 writing/journal_manuscript/manuscript.tex
Finish full draft

\begin{abstract}
%To communicate successfully, speakers must flexibly adapt %the specificity of 
%their utterances to the demands of the current context. When they are unsure exactly which objects are in view of their partner, for example, they may provide additional disambiguating information when referring to a particular object: saying "cassette tape" instead of the potentially ambiguous ``tape."
Recent debates over adult theory of mind use have hinged on natural-language communication tasks with knowledge asymmetries, but have largely neglected the nuanced pragmatics of these tasks. These pragmatic considerations . In particular, using occluded objects to create perspective asymmetries may have unexpected side effects under pragmatic reasoning. Cooperative speakers ought to flexibly adjust their utterances to be more informative uncertainty about what is in the listener's field of view. In a direct replication, we show that scripted confederates violate these expectations by using less informative labels than unscripted directors naturally use. In a follow-up experiment, we directly manipulate whether objects are hidden to test the pragmatic account of speaker informativity in uncertain environments. Hence, apparent failures of visual perspective-taking may in fact be successes for sophisticated theory of mind use in context. Language is well-tuned to deal with knowledge mismatch, and perspective neglect is just part of that.
%Recent theories of language use as recursive social reasoning remain in tension with evidence that adult listeners apparently fail to take their partner's perspective in communication. To reconcile these points of view, we use a computational model of communication under uncertainty to analyze the pragmatic demands of a common theory of mind test.  Through a minimal pair of replications comparing scripted vs. unscripted speakers, we show that scripted confederates used in previous studies are \emph{uncooperative}: they are less informative than what a speaker would actually produce in that situation, thus violating the listener's rational social expectations. This ironically shows that apparent failures of theory of mind are in fact attributable to sophisticated expectations about speaker behavior---that is, to theory of mind. 
\end{abstract}

@@

% Discuss other criticisms of Keysar paradigm?
%While these results are compelling, the paradigm has been criticized from few different angles. 
%\cite{HellerGrodnerTanenhaus08_Perspective} have pointed out that in many cases, the hidden object was a better fit for the referring expression than the one in common ground (e.g. the hidden roll of tape vs. the cassette tape for ``the tape''), making the hidden object \emph{a priori} more likely to be the referent; it would generally be fairer to compare two objects that fit the referring expression equally well. 
%We validate this argument by empirically measuring relative fit of the expressions to the target and distractor items.
%Moreover, \cite{HannaTanenhausTrueswell03_CommonGroundPerspective, HannaTanenhaus04_PragmaticEffects} argued that the viewpoint asymmetry paradigm is somewhat unnatural: common ground is typically built incrementally over the course of an interaction rather than presented all at once, and it is rare for a shared display to differ in perceptual accessibility.

@@

We recruited 368 participants (196 pairs) from Amazon Mechanical Turk to play an interactive communication game using the framework described in \cite{Hawkins15_RealTimeWebExperiments}. 58 pairs were unable to complete the game due to a server outage. Following our preregistered exclusion criteria\footnote{Unless otherwise mentioned, all analyses and \dots are preregistered at \textrm{https://osf.io/qwkmp/}}, we also removed 13 games who reported confusion or made two or more errors on filler items and 2 additional games containing non-native English speakers. This left 127 pairs in our final sample. \todo[inline]{rxdh: also mention removal of 3 games only using location or using 'taboo' utterances.}

@@

Finally, we consider the link between the speaker and listener behavior we observed across condition. To what extent does the informativity of speaker utterances account for the substantial variance across items we observed in listener errors in the two conditions? While a naive perspective-taking account would predict no relationship, a perspective-negligence account predicts that listeners simply pick the object that fits the description best regardless of whether it is hidden or not. Indeed, we found a strong negative correlation between informativity and error rates: listeners make fewer errors when utterances are a better fit for the target relative to the distractor ($\rho = -0.8$, bootstrapped 95\% CI $= [-0.89, -0.69]$; Fig. \ref{fig:exp1speaker}B). %  We used a mixed effects logistic regression model to estimate the effect of target and distractor fit on the probability of making a critical error in both experiments, including a random intercept for game ID. We found that participants are less likely to make errors when informativity is higher. Furthermore, a model including target fit and distractor fit in addition to item-level fixed effects is significantly better than a model including item alone, $\chi^2(2) = XXX, p < YYY$, implying that speaker informativity captures residual variance beyond the item-wise effects reported above.
\todo[inline]{rxdh: I think this bootstrapped correlation stat at the objectSet-condition level makes this point well enough for our purposes (it's a pretty huge effect...), but I could also do a fancier thing boostrapping logistic coefficients at the trial-by-trial level if necessary. }
\todo[inline]{rxdh: also, is it worth having a short appendix with more details on the multi-stage bootstrapping procedure? it's very straightforward but takes a few sentences to explain\dots}

@@

In both raw patterns of error and mouse-tracking metrics, we successfully replicated the findings of \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}. Participants frequently attempted to move the occluded alternative when it matched the target referential expression, even though the director couldn't possibly have been referring to it, even on trials where they moved the correct object, matchers were more likely to hover their cursor over the occluded cell. Furthermore, in a novel analysis of utterance informativity, we found that patterns of errors across items are well-predicted by relative fit to the target vs. distractor. Taken together, these results support the claim that listeners neglect the speaker's perspective.

At the same time, however, our \emph{speaker} results suggest a deeper explanation for the phenomenon of perspective-neglect. We found a tendency toward additional, possibly unnecessary, informativity in speaker descriptions. For example, instead of the scripted ``move the \emph{brush} one square to the right'' which would be sufficient with only one brush in their display, speakers instead chose to give descriptions like ``move the \emph{hairbrush with two lines on the handle} to the right.'' 
Perhaps speakers were taking the time to make more precise descriptions than required by their own immediate display because they believed it was contextually relevant. 
In particular, speakers know that there additional objects of unknown identity in their partner's field of view, potentially increasing the risk of miscommunication from imprecise descriptions. 
If natural speakers do adaptively produce more informative descriptions in context, then pragmatic listeners expecting speakers to do so may be justified in weighting considerations of the speaker's visual perspective less strongly.

@@

  \begin{figure}[t!]
 \begin{center}
 \vspace{-.5cm}
 \includegraphics[scale=.35]{figures/Exp2_design.pdf}
 \caption{Within-pair factorial design used in Exp.~2. In the common condition, we reproduce a simple pragmatic reference contrast: when more than one star is present in common ground, speakers are expected to be more informative. On hidden versions of these condition, the same set of objects is visible, but some additional squares are occluded. If pragmatic directors represent uncertainty over what the matcher sees behind these squares, we predict that they will produce more informative utterances.}
 \vspace{-.5cm}
 \label{fig:exp2design}
 \end{center}
 \end{figure}

@@

What are these additional words spent on describing? As a secondary analysis, we annotated each utterance by which object features were mentioned (shape, texture, color). Speakers nearly always mentioned shape  (e.g. `star', `triangle') as the head noun of their referring expression regardless of context, so differences in words across conditions must be due to providing additional information about color and texture. We ran separate mixed-effect logistic regressions for color and texture predicting mention from context; due to well-known convergence issues in logistic models, the maximum random effect structure supported by our data contains only speaker-level intercepts and slopes for occlusion. In both cases, we found simple effects of occlusion in far contexts ($b = 1.33, z = 2.9, p = 0.004$ for color; $b = 2.1, z = 5.7, p < 0.001$ for texture, see Fig. \ref{fig:exp2results}B). In other words, in displays like the one in Fig. \ref{fig:exp2results}A where the target was the only star, speakers were slightly more likely to produce the star's color---and substantially more likely to produce its texture---when there were occlusions present even though the visible objects were exactly the same.

@@

@@

Pragmatic language understanding requires sophisticated social reasoning. To interpret an utterance, a listener must consider how a speaker is likely to behave in context.
The rational use of theory of mind for a listener thus depends on her expectations about the speaker: If, in a particular context, she expects a speaker to provide sufficiently informative utterances, she may be justified in neglecting his epistemic state when resolving reference.

% 
In our replication, we found empirical support for the claim that listeners neglect the speaker's epistemic state in some contexts, as claimed by \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}: when the speaker's utterance fit the hidden distractor better than the target, matchers were more likely to make errors. 
Indeed, we found that the extremely heterogeneous pattern of errors across items was well explained by the relative fit of the utterance to target and distractor.
This suggests that reference disambiguation was driven primarily by \emph{a priori} label fitness rather than consideration of occluded vs. mutually visible items.

However, this finding does \emph{not} necessarily imply limitations on theory of mind. Speakers systematically provide more informative utterances in contexts where views are uncertain, hence listeners with well-calibrated social expectations are justified in neglecting perspective. Rather than debating provide a principled, rational explanation of \emph{why} listeners may neglect speaker perspective in the first place. These reasons stem from more sophisticated pragmatic expectations than simple consideration of perspective, thereby opening a deeper avenue by which theory of mind use guides flexible communication. % if speakers could be expected to naturally provide expressions which apply better to the target, then this behavior would be appropriate.
% If listeners arrive at this interpretation strategy through pragmatic reasoning, then neglecting the speaker's epistemic state would be rational and also the result of theory of mind use.

@@

% 1. Tying back to original expt (e.g. pitch Expt. 3 idea). Listeners didn't know what's going on when they heard the dramatically under-informative `tape' -- one direction for future work is to directly manipulate expectations about speakers...

% 2. Other reasons for over-informativity (e.g. Judith stuff)

% 3. Relationship to Heller model, Rubio-Fernandez, other critiques of Keysar?

% 4. 
%%%%%%%

The Gricean maxim of quality dictates that cooperative speakers should make their utterance as informative as is required for current purposes, but no more so. If the referring expressions used in by confederates uniquely pick out the target from the speaker's perspective, then why our unscripted speakers be more informative than this? 
%strictly necessary and why would listeners come to expect such ``overinformativity''? 
One possibility, which we tested in Exp. 2, is that awareness of the complex mismatch in epistemic state with the listener leads the speaker to provide extra information in an attempt to avoid miscommunication.
Another possibility is that more general dynamics of language are in play.
Studies of over-informativity in referring expressions have uncovered a general tendency of speakers to provide redundant information.
This tendency can depend on a number of situational factors, such as the tendency to mention perceptually salient features to speed up the identification process  \cite{KoolenGattGoudbeekKrahmer11_Overspecification}. 
%In the current task, it seems particularly relevant that both participants knew about the presence of hidden objects, increasing uncertainty about possible distractors and placing additional pressure on the speaker to overspecify. 
The exact origin is a subject that must be followed up by future research \cite[e.g.]{GannBarr14_AudienceDesign}, but it is clear that the tendency of speakers to produce highly informative referring expressions is useful to, and relied on by, listeners. 
%Indeed, the remaining errors in Expt.~2 are at least partially due to the lack of availability of more specific expressions. 
%The items on which errors were most likely in Expt.~2 were difficult precisely because the natural utterance was \emph{still} ambiguous: even if the speaker uses ``hairbrush'' instead of the basic-level ``brush,'' for example, the distractor remains a more typical exemplar of the subcategory.

@@

It is worth noting several significant differences between our study and \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}.
The primary difference between our study and the original, of course, is that it was run on the web with participants connected through a virtual environment, instead of face-to-face in a room. We believe we addressed the major concern about exploring theory of mind in web experiments -- that participants do not truly believe they are interacting with another human -- by allowing instantaneous, responsive, real-time interaction.  On the other hand, it is known that textual communication, as in our chat box, can differ from face-to-face verbal communication. Additionally, we omitted the procedural step of placing the hidden distractor in a paper bag, and some aspects of the interface such as the graphical representation of occluded cells may be less intuitive, or require more training, on the web than in the lab. % Directors watched objects move through the actual moment-by-moment mouse trajectories that matchers used to drag them, and matchers saw the actual timing of the messages sent by the director.

A related difference is our decision not to use a confederate. While confederates are useful for reducing variation across instances of the experiment and delivering carefully targeted manipulations, their use may have unexpected consequences. Beyond the difficulties of conducting large-scale experiments with confederates, it is difficult to exactly replicate all the subtleties of the confederate's behavior that might influence results. The pair of experiments we report is a reminder that manipulations administered by a trained confederate can interact in unexpected ways with a participant's social and communicative expectations. Regardless of the experimental context, it is illuminating to see how real participants naturally interact.

\todo[inline]{mention rubio fernandez early?}
Using similar reasoning, \cite{RubioFernandez16_DirectorTaskAttention} showed that listeners became suspicious of what was actually in common ground after hearing overinformative utterances, thus successfully using theory of mind reasoning.

\todo[inline]{Mention Westra \& Carruthers as another critique focusing on pragmatics?}

\todo[inline]{Mention neural coordination papers? e.g. Stephens et al 2010, Stolk et al, 2014?}

>>>>

\begin{abstract}
%To communicate successfully, speakers must flexibly adapt %the specificity of 
%their utterances to the demands of the current context. When they are unsure exactly which objects are in view of their partner, for example, they may provide additional disambiguating information when referring to a particular object: saying "cassette tape" instead of the potentially ambiguous ``tape."
Recent debates over adult theory of mind use have hinged on natural-language communication tasks with knowledge asymmetries, but have largely neglected the nuanced pragmatics of these tasks.  In particular, using occluded objects to create perspective asymmetries may have unexpected side effects under pragmatic reasoning. Cooperative speakers ought to flexibly adjust their utterances to be more informative uncertainty about what is in the listener's field of view. In a direct replication, we show that scripted confederates violate these expectations by using less informative labels than unscripted directors naturally use. In a follow-up experiment, we directly manipulate whether objects are hidden to test the pragmatic account of speaker informativity in uncertain environments. Hence, apparent failures of visual perspective-taking may in fact be successes for sophisticated theory of mind use in context. Language is well-tuned to deal with knowledge mismatch, and perspective neglect is just part of that.
%Recent theories of language use as recursive social reasoning remain in tension with evidence that adult listeners apparently fail to take their partner's perspective in communication. To reconcile these points of view, we use a computational model of communication under uncertainty to analyze the pragmatic demands of a common theory of mind test.  Through a minimal pair of replications comparing scripted vs. unscripted speakers, we show that scripted confederates used in previous studies are \emph{uncooperative}: they are less informative than what a speaker would actually produce in that situation, thus violating the listener's rational social expectations. This ironically shows that apparent failures of theory of mind are in fact attributable to sophisticated expectations about speaker behavior---that is, to theory of mind. 
\end{abstract}

@@

% Discuss other criticisms of Keysar paradigm?
%While these results are compelling, the paradigm has been criticized from few different angles. 
%\cite{} have pointed out that in many cases, the hidden object was a better fit for the referring expression than the one in common ground (e.g. the hidden roll of tape vs. the cassette tape for ``the tape''), making the hidden object \emph{a priori} more likely to be the referent; it would generally be fairer to compare two objects that fit the referring expression equally well. 
%We validate this argument by empirically measuring relative fit of the expressions to the target and distractor items.
%Moreover,  argued that the viewpoint asymmetry paradigm is somewhat unnatural: common ground is typically built incrementally over the course of an interaction rather than presented all at once, and it is rare for a shared display to differ in perceptual accessibility.

@@

We recruited 368 participants (196 pairs) from Amazon Mechanical Turk to play an interactive communication game using the framework described in \cite{Hawkins15_RealTimeWebExperiments}. 58 pairs were unable to complete the game due to a server outage. Following our preregistered exclusion criteria\footnote{Unless otherwise mentioned, all analyses and \dots are preregistered at \textrm{https://osf.io/qwkmp/}}, we also removed 13 games who reported confusion or made two or more errors on filler items and 2 additional games containing non-native English speakers. This left 127 pairs in our final sample. \todo[inline]{TODO: also mention removal of 3 games only using location or using 'taboo' utterances (i.e. cryptic clues).}

@@

%While a naive perspective-taking account would predict no relationship, a perspective-negligence account predicts that listeners simply pick the object that fits the description best regardless of whether it is hidden or not.
Finally, we consider the link between the speaker and listener behavior we observed across condition. To what extent does the informativity of speaker utterances account for the substantial variance across items we observed in listener errors in the two conditions? We found a strong negative correlation between informativity and error rates: listeners make fewer errors when utterances are a better fit for the target relative to the distractor ($\rho = -0.8$, bootstrapped 95\% CI $= [-0.89, -0.69]$; Fig. \ref{fig:exp1speaker}B). This suggests that reference disambiguation was driven primarily by \emph{a priori} label fitness rather than consideration of occluded vs. mutually visible items. 
 %  We used a mixed effects logistic regression model to estimate the effect of target and distractor fit on the probability of making a critical error in both experiments, including a random intercept for game ID. We found that participants are less likely to make errors when informativity is higher. Furthermore, a model including target fit and distractor fit in addition to item-level fixed effects is significantly better than a model including item alone, $\chi^2(2) = XXX, p < YYY$, implying that speaker informativity captures residual variance beyond the item-wise effects reported above.
\todo[inline]{rxdh: I think this bootstrapped correlation stat at the objectSet-condition level makes this point well enough for our purposes (it's a pretty huge effect...), but I could also do a fancier thing boostrapping logistic coefficients at the trial-by-trial level if necessary. }
\todo[inline]{rxdh: also, is it worth having a short appendix with more details on the multi-stage bootstrapping procedure? it's very straightforward but takes a few sentences to explain\dots}

@@

In both raw patterns of error and mouse-tracking metrics, we successfully replicated the findings of \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}. Participants frequently attempted to move the occluded alternative when it matched the target referential expression, even though the director couldn't possibly have been referring to it. And even on trials where they moved the correct object, matchers were more likely to hover their cursor over the occluded cell. Furthermore, by considering utterance informativity, we found that patterns of errors across items are well-predicted by relative fit to the target vs. distractor. Taken together, these results support the claim that listeners neglect the speaker's perspective in some contexts.

At the same time, however, our \emph{speaker} results suggest a deeper explanation for the phenomenon of perspective-neglect. We found a tendency toward additional, possibly unnecessary, informativity in speaker descriptions. For example, instead of the scripted ``move the \emph{brush} one square to the right'' which would be sufficient with only one brush in their display, speakers instead chose to give descriptions like ``move the \emph{hairbrush with two lines on the handle} to the right.'' 
Perhaps speakers were taking the time to make more precise descriptions than required by their own immediate display because they believed it was contextually relevant. 
In particular, speakers know that there additional objects of unknown identity in their partner's field of view, potentially increasing the risk of miscommunication from imprecise descriptions. 
If natural speakers do adaptively produce more informative descriptions in context, then pragmatic listeners rationally expecting speakers to do so may be justified in weighting considerations of the speaker's visual perspective less strongly.

@@

  \begin{figure}[t!]
 \begin{center}
 \vspace{-.5cm}
 \includegraphics[scale=.35]{figures/Exp2_design.pdf}
 \caption{Within-pair factorial design used in Exp.~2. In the common condition, we reproduce a simple pragmatic reference contrast: when more than one star is present in common ground, speakers are expected to be more informative. On hidden versions of these condition, the same set of objects is visible, but some additional squares are occluded. If pragmatic directors represent uncertainty over what the matcher sees behind these squares, we predict that they will produce more informative utterances. \todo[inline]{TODO: Use screenshots of real displays instead of cartoon.}}
 \vspace{-.5cm}
 \label{fig:exp2design}
 \end{center}
 \end{figure}

@@

What are these additional words spent on describing? As a secondary analysis, we annotated each utterance by which object features were mentioned (shape, texture, color). Speakers nearly always mentioned shape  (e.g. `star', `triangle') as the head noun of their referring expression regardless of context, so differences in words across conditions must be due to providing additional information about color and texture. We ran separate mixed-effect logistic regressions for color and texture predicting mention from context; due to well-known convergence issues in logistic models, the maximum random effect structure supported by our data contains only speaker-level intercepts and slopes for occlusion. In both cases, we found simple effects of occlusion in far contexts ($b = 1.33, z = 2.9, p = 0.004$ for color; $b = 2.1, z = 5.7, p < 0.001$ for texture, see Fig. \ref{fig:exp2results}B). In other words, in displays like the one in Fig. \ref{fig:exp2results}A where the target was the only `star', speakers were slightly more likely to produce the star's color---and substantially more likely to produce its texture---when there were occlusions present, even though the visible objects were exactly the same.

@@

We found in Expt.~1 that speakers naturally produced more informative utterances than would be necessary given the set of objects in their visual field. In Expt.~2 we directly tested the hypothesis that increased informativity is due to uncertainty about the listener's view imposed by the presence of occlusions. By manipulating occlusions, we found that speakers are not only context-sensitive in choosing referring expressions that are appropriately distinguishing in a shared context, but also \emph{occlusion-sensitive} in adaptively compensating for additional uncertainty by adding additional information. These forms of sensitivity are difficult to explain under an egocentric theory: speakers were spontaneously willing to spend additional time and keystrokes to give information that would be redundant given the set of objects visible in their own display.

@@

The rational use of theory of mind for a listener extends well beyond simple consideration of who sees what; it depends on her ability to reason holistically about the speaker's likely communicative behavior in context. 
%Pragmatic language understanding depends upon social reasoning. To interpret an utterance, a listener must consider how a speaker is likely to behave in context; to produce an utterance, a speaker must consider how the listener is likely to understand it.
In this paper, we considered the hypothesis that successes in this broader Gricean application of theory of mind may ironically explain apparent failures to account for visual perspective. 
In a direct replication, we found strong empirical support for the claim that listeners neglect the speaker's perspective in some contexts. 
Rather than debating the existence of this phenomenon, then, we suggested an alternative, non-egocentric explanation of \emph{when} and \emph{why} listeners may neglect speaker perspective in the first place. 
In particular, while the scripted instructions in Exp.~1 systematically violated Gricean expectations of cooperativity, natural speakers did not. They appropriately increased the informativity of their referring expressions to account for occlusions in context. 
Our demonstrations of speaker occlusion-sensitivity thus provide justification for relying on speakers to be informative.

% 1. Tying back to original expt (e.g. pitch Expt. 3 idea). 
If visual perspective-taking is as effortful and cognitively demanding as claimed \cite{LinKeysarEpley10_ReflexivelyMindblind}, then pragmatic reasoning may play an important role in how listeners rationally allocate their resources during communication \cite{GriffithsLiederGoodman15_LevelsOfAnalysis}. Using theory of mind to form early expectations about how speakers are likely to behave in context allows listeners to adopt a more efficient strategy in the long-term. An important direction for future work, then, is to evaluate the causal role of pragmatic reasoning by directly manipulating the listener's Gricean expectations. We hypothesize that listeners would flexibly choose to rely more heavily on perspective information if they could not rely on their partner to be cooperative. In fact, one explanation for why error rates in our replication were higher than the original is the influence of the `filler' trials where speakers in the scripted condition were allowed to freely produce referring expressions. Many speakers were producing long, highly informative utterances in these filler trials, potentially setting up strong expectations for cooperativity that were then flouted in critical trials.

%These reasons stem from more sophisticated pragmatic expectations than simple consideration of perspective, thereby opening a deeper avenue by which theory of mind use guides flexible communication. % if speakers could be expected to naturally provide expressions which apply better to the target, then this behavior would be appropriate. a listener expects a speaker to provide sufficiently informative utterances, she may be justified in neglecting his visual perspective when resolving reference. We predict that

%However, this finding does \emph{not} necessarily imply limitations on theory of mind. Speakers systematically provide more informative utterances in contexts where views are uncertain, hence listeners with well-calibrated social expectations are justified in neglecting perspective.
There is a long history of debate over both the methods and interpretation of the director-matcher task \cite[e.g.]{HannaTanenhausTrueswell03_CommonGroundPerspective, HannaTanenhaus04_PragmaticEffects, HellerGrodnerTanenhaus08_Perspective, BrownSchmidtTanenhaus08_TargetedGame}. Our findings are particularly resonant with several recent results. \cite{RubioFernandez16_DirectorTaskAttention} secretly scrambled occlusions across the speaker's and listener's screens to create a mismatch in expectations about which objects are shared. Listeners were able to gradually infer this manipulation from the speaker's choice of referring expressions, implicating Gricean theory of mind reasoning about what is appropriate or inappropriate to say in context. Modeling work by \cite{HellerParisienStevenson16_ProbabilisticWeighing} (see also \cite{MozuraitisEtAl18_ProductionCombination}) has argued that speakers and listeners are probabilistically weighting their own egocentric visual perspective along with their partner's perspective. An open question raised by these studies is how that weighting parameter is determined in a given context. Our results suggest that Gricean reasoning may play an important role.

%These reasons stem from more sophisticated pragmatic expectations than simple consideration of perspective, thereby opening a deeper avenue by which theory of mind use guides flexible communication. 
% if speakers could be expected to naturally provide expressions which apply better to the target, then this behavior would be appropriate.
% If listeners arrive at this interpretation strategy through pragmatic reasoning, then neglecting the speaker's epistemic state would be rational and also the result of theory of mind use.

@@

% 2. Other reasons for over-informativity (e.g. Judith stuff)
%%%%%%%

%The Gricean maxim of quality dictates that cooperative speakers should make their utterance as informative as is required for current purposes, but no more so. If the referring expressions used in by confederates uniquely pick out the target from the speaker's perspective, then why our unscripted speakers be more informative than this? 
%strictly necessary and why would listeners come to expect such ``overinformativity''? 
%One possibility, which we tested in Exp. 2, is that awareness of the complex mismatch in epistemic state with the listener leads the speaker to provide extra information in an attempt to avoid miscommunication.
Finally, while we are not often in communication scenarios with such explicitly marked occluders, we are near constantly in a state of uncertainty over what is in our partner's visual context. The occlusion-sensitivity we observed in Exp. 2 is representative of how pragmatic mechanisms help solve this problem.
Studies of over-informativity in referring expressions have uncovered a general tendency of speakers to provide redundant information.
This tendency can depend on a number of situational factors, such as the tendency to mention perceptually salient features to speed up the identification process  \cite{KoolenGattGoudbeekKrahmer11_Overspecification}. 
%In the current task, it seems particularly relevant that both participants knew about the presence of hidden objects, increasing uncertainty about possible distractors and placing additional pressure on the speaker to overspecify. 
The exact origin of this behavior is a subject that must be followed up by future research \cite[e.g.]{GannBarr14_AudienceDesign}, but it is clear that the tendency of speakers to produce highly informative referring expressions is useful to, and relied on by, listeners. 
%Indeed, the remaining errors in Expt.~2 are at least partially due to the lack of availability of more specific expressions. 
%The items on which errors were most likely in Expt.~2 were difficult precisely because the natural utterance was \emph{still} ambiguous: even if the speaker uses ``hairbrush'' instead of the basic-level ``brush,'' for example, the distractor remains a more typical exemplar of the subcategory.

@@

%It is worth noting several significant differences between our study and \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}.
%The primary difference between our study and the original, of course, is that it was run on the web with participants connected through a virtual environment, instead of face-to-face in a room. We believe we addressed the major concern about exploring theory of mind in web experiments -- that participants do not truly believe they are interacting with another human -- by allowing instantaneous, responsive, real-time interaction.  On the other hand, it is known that textual communication, as in our chat box, can differ from face-to-face verbal communication. Additionally, we omitted the procedural step of placing the hidden distractor in a paper bag, and some aspects of the interface such as the graphical representation of occluded cells may be less intuitive, or require more training, on the web than in the lab. % Directors watched objects move through the actual moment-by-moment mouse trajectories that matchers used to drag them, and matchers saw the actual timing of the messages sent by the director.

%Finally, a key aspect of our approach was our decision not to use a confederate. While confederates are useful for reducing variation across instances of the experiment and delivering carefully targeted manipulations, their use may have unexpected consequences. Beyond the difficulties of conducting large-scale experiments with confederates, it is difficult to exactly replicate all the subtleties of the confederate's behavior that might influence results. The pair of experiments we report is a reminder that manipulations administered by a trained confederate can interact in unexpected ways with a participant's social and communicative expectations.

\todo[inline]{End with something punchy?}

%\todo[inline]{Mention neural coordination papers? e.g. Stephens et al 2010, Stolk et al, 2014?}
